\textsf{Are large language models superhuman chemists?}

### 2024-03-25 src/tex/ms.tex
contrastive -> divergent

However, the rapid increase in capabilities of chemical \gls{ml} models led (even before the recent interest in \glspl{llm}) to concerns about the potential for dual use of these technologies, e.g., for the design of chemical weapons.\autocite{gopal2023releasing, ganguli2022red, Urbina_2022, campbell2023censoring, moulange2023towards, urbina2022teachable}
To some extent, this is not surprising as any technology that can be used to predict the toxicity of a compound for drug discovery, can be used in a contrastive way in chemical warfare.
Moreover, it is important to realize that the user base of such models is not only limited to experts in chemistry and materials science who critically reflect every output such models produce. 
For example, many students frequently consolidate those tools---perhaps even to prepare chemical experiments.\autocite{Intelligent.com_2023}
This also implies to users from the general public, who might consider using \glspl{llm} to answer questions about the safety of chemicals.
Thus, for some users, misleading information---especially about safety-related aspects---might lead to harmful outcomes. 
However, even for experts, the chemical understanding and reasoning capabilities are important as they will determine the capabilities and limitations of their models in their work, e.g., in copilot systems for chemists.
Unfortunately, apart from anecdotal reports, there is little evidence on how \glspl{llm} perform compared to experts.

>>>>

However, the rapid increase in capabilities of chemical \gls{ml} models led (even before the recent interest in \glspl{llm}) to concerns about the potential for dual use of these technologies, e.g., for the design of chemical weapons.\autocite{gopal2023releasing, ganguli2022red, Urbina_2022, campbell2023censoring, moulange2023towards, urbina2022teachable}
To some extent, this is not surprising as any technology that can be used to predict the toxicity of a compound for drug discovery, can be used in a divergent manner in chemical warfare.
Moreover, it is important to realize that the user base of such models is not only limited to experts in chemistry and materials science who critically reflect every output such models produce. 
For example, many students frequently consolidate those tools---perhaps even to prepare chemical experiments.\autocite{Intelligent.com_2023}
This also implies to users from the general public, who might consider using \glspl{llm} to answer questions about the safety of chemicals.
Thus, for some users, misleading information---especially about safety-related aspects---might lead to harmful outcomes. 
However, even for experts, the chemical understanding and reasoning capabilities are important as they will determine the capabilities and limitations of their models in their work, e.g., in copilot systems for chemists.
Unfortunately, apart from anecdotal reports, there is little evidence on how \glspl{llm} perform compared to experts.
